\renewcommand{\theequation}{\theenumi}
\begin{enumerate}[label=\thesection.\arabic*.,ref=\thesection.\theenumi]
\numberwithin{equation}{enumi}

\item aigiri.txt contains a slokam in Telugu it is read and all the characters are stored to the variable $sloka\_txt$ with the help of the code below.
\begin{lstlisting}[language=Python]
sloka = open('aigiri.txt', 'r') 
sloka_txt = sloka.read() 
sloka.close()
\end{lstlisting}

\item $sloka\_txt$ is a string containing all the words it is split into individual words and the list of words are saved to the variable $words$. A new file $unicode.txt$ is opened to write the converted unicode.
\begin{lstlisting}[language=Python]
words = sloka_txt.split() 
uni_file = open('unicode.txt', 'w')
\end{lstlisting}

\item A  for loop runs through all the words in the list and checks if the word is $'|'$ or a number. If so it does not convert the word to its unicode value and proceeds with the next word. If the word is neither $'|'$ nor a number, an other for loop is used to access each character of the word. Each character is then passed on to a function called $ord()$ which returns the integer code point value of the character. The integer value is then converted to its hexadecimal value using the function $hex()$. The hexadecimal string contains the character $'x'$ which is replaced with a null character to get the actual hexadecimal value it is then appedned to the string $'U+'$ and the resultant is written onto the txt file. The process is repeated for the remaining characters in the word and for all the remaining words.
\begin{lstlisting}[language=Python]
for i in words:
	if(i !='|' and not(i.isdigit())):
	for j in i:
		uni_file.write('U+' + 
		hex(ord(j)).replace('x', ''))
		uni_file.write(' ') 
uni_file.close()
\end{lstlisting} 

\end{enumerate}
